Simple Approximation Algorithms for Partitional and Hierarchical Clustering

### 2015-05-11 tex/project.tex
Last results and computer specs in report
Added sentence to conclusion

Tests were conducted using Python 2.7.9 on a 64-bit Windows platform, on a 4 core Intel processor. Results are given in Figure 2  below with some results averaged due to space constraints.

@@

\section{Conclusion and Future Work}
For partitional clustering, we found that the approximation algorithms in the literature are in general slower and cannot improve much on current heuristics used despite their approximation guarantees. This was not true in the hierarchical clustering case where we saw significant improvement in FScore measures for our implemented methods and overall good approximation ratios where none were had before. In particular, our logarithmic nesting algorithm seems to provide the best balance between performance and computational efficiency.

>>>>

Tests were conducted using Python 2.7.9 on a 64-bit Windows platform, on a 4 core 3.4 Ghz Intel i7 processor with 16 GB physical memory. Results are given in Figure 2  below with some results averaged due to space constraints.

@@

\section{Conclusion and Future Work}
We implemented various simple approximation algorithms for partitional clustering, and a framework for hierarchical clustering.  We compared these algorithms, along with heuristic modifications, against the most common clustering algorithms used in practice.

For partitional clustering, we found that the approximation algorithms in the literature are in general slower and cannot improve much on current heuristics used despite their approximation guarantees. This was not true in the hierarchical clustering case where we saw significant improvement in FScore measures for our implemented methods and overall good approximation ratios where none were had before. In particular, our logarithmic nesting algorithm seems to provide the best balance between performance and computational efficiency.
